---
title: "My Shiny App"
author: "Mariam Mohamed"
date: "12/19/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## App Idea

This app's goal is to plot the iris dataset sepal length and width and plot petal length and width according to the species selected by the user.

## Iris species to choose from

- virginica
- setosa
- versicolor

The user has to choose from the list and click on the submit button

## Example: Sepal.Length ~ Sepal.Width: using only species ["virginica", "setosa"]

```{r , echo=FALSE}
library(ggplot2)
```

```{r ,echo = FALSE}
my.data <- iris[iris$Species %in% c("virginica", "setosa"), ]
qplot(Sepal.Length, Sepal.Width, xlab = "Sepal.Length", ylab = "Sepal.Width", colour=Species, data = my.data)
```

## Example: Petal.Length ~ Petal.Width: using species ["virginica", "setosa", "versicolor"]


```{r ,echo = FALSE}
my.data <- iris[iris$Species %in% c("virginica", "setosa", "versicolor"), ]
qplot(Petal.Length, Petal.Width, xlab = "Petal.Length", ylab = "Petal.Width", colour=Species, data = my.data)
```


